Resonant states for quantum ring with two infinite leads

### 2016-03-18 ddays/DD16_gerasimovda.tex
Updated the s matrix formula
Draw graph

\title{Title of paper}

\author{Author A.B., \textbf{Author B.A.}} % presenting author is marked out by \textbf 
{Institute1, address1\\ e-mail: {\tt usernameA@example.com, usernameB@example.com} }

% for name index
\index{Author, A.B.} 
\index{Author, B.A.}

\coauthor{Author C.B.} {Institute2, address2\\ e-mail: {\tt usernameC@example.com}}

\index{Author, C.B.}

%OR

%\def\supind#1{${}^\mathrm{#1}$}
%
%\author{Author A.B.\supind{1,2}, \textbf{Author B.A.}\supind{1}, Author C.B.\supind{2,3}}
%{\supind{1}Institute1, address1\\ \supind{2}Institute2, address2\\ \supind{3}Institute3,
%address3\\e-mail: {\tt usernameA@example.com, usernameB@example.com,
%usernameC@example.com} }
%
%\index{Author, A.B.} \index{Author, B.C.} \index{Author, C.B.}

Text of abstract

\medskip

\centerline{\includegraphics[width=80mm]{fig_example}}

\medskip

{\narrower\noindent \textbf{Fig.~1:} Text of long caption.\par}

\medskip

%\centerline{\textbf{Fig. 1:} Text of short caption.}

@@

\bibitem{1} A. Author, B. Author, \textit{Some good book}, Some University Press, Some City
(2010).

\bibitem{2} C. Author, \textit{Journal of Something}, \textbf{90}, 34--42 (2003).

>>>>

\title{Resonant states for quantum ring with two infinite leads}

\author{\textbf{Gerasimov D.A.}, Popov I.Yu., Popov A.I.} % presenting author is marked out by \textbf 
{Department of Higher Mathematics, ITMO University, Saint Petersburg 197101,
Russia\\ e-mail: {\tt karlicoss@gmail.com, popov1955@gmail.com, popov239@gmail.com} }

% for name index
\index{Gerasimov, D.A.} 
\index{Popov, I.Yu.}
\index{Popov, A.I.}

\newcommand\abs[1]{\left|#1\right|}

Quantum graph is a widely used model of nanosystem [1-4]. If the graph $\Gamma$ consists of finite number of edges of finite lengths, then the Hamiltonian has purely discrete spectrum and the eigenfunctions are complete in $L_2(\Gamma)$. If $\Gamma$ contains semi-infinite edges, one has non-empty continuous spectrum and resonances generated by the eigenvalues of the Hamiltonian of finite graph. For many applications, it is important to know a space in which the resonant states form a complete system. In this paper we determine this space for a graph with two infinite leads and a loop (Fig.~1) using Sz.-Nagy model [5].

\medskip
\centerline{\includegraphics[width=120mm]{graph.eps}}
\medskip
{\narrower\noindent \textbf{Fig.~1:}
Quantum graph $\Gamma$ consisting of edges $\Omega_{inc}, \Omega_{out}, \Omega_1, \Omega_2$. $\Omega_1$ and $\Omega_2$ represent the 1D ring connected to lead $\Omega_{inc}$ via the vertex $V_{inc}$ and to lead $\Omega_{out}$ via $V_{out}$.
\par}
\medskip
% $-\psi'_{inc}(V_{inc}) + \psi_1'(V_{inc}) + \psi_2'(V_{inc}) = a \psi_{inc}(V_{inc})$; $\psi'_{out}(V_{out}) - \psi_1'(V_{out}) - \psi_2'(V_{out}) = a \psi_{out}(V_{out}) $
We are interested in scattering of a wave with wavevector $k$ incoming from the left lead to the right one. At vertices $V_{inc}, V_{out}$ we impose Dirichlet boundary conditions for wavefunctions and $\delta$-coupling boundary conditions with the coupling constant $a$ for wavefunction's derivative.
After solving the system of equations, we obtain a closed-form expression for the S-matrix determinant:
\[
\det S = \frac{((a^2 - 5k^2) \cos(kd) \sin(kd) -4ak \sin^2(kd) + 2ak) + i (2ak \cos(kd) \sin(kd) -4k^2 \sin^2(kd) + 2k^2)}{((a^2 - 5k^2) \cos(kd) \sin(kd) -4ak \sin^2(kd) + 2ak) - i (2ak \cos(kd) \sin(kd) -4k^2 \sin^2(kd) + 2k^2)}
\]

To establish the completeness, we have to prove that $S$ is a Blaschke-Potapov product [6], that is, $\lim\limits_{r \to 1 - 0} \int\limits_{L_r} \log  \abs{\det S(k)} \frac{dk}{(k - 1)^2} = 0$, where $L_r$ is the image of the curve $\abs{\xi} = r$ ($r < 1$) under the map $k = i \frac{1 + \xi}{1 - \xi}$. Substituting $\det S$, which we calculated above, and estimating the integral, one obtains the desired result.

This work was partially financially supported by the Government of the Russian Federation (grant 074-U01), by Ministry of Science and Education of the Russian Federation (GOSZADANIE 2014/190, Projects No 14.Z50.31.0031 and No. 1.754.2014/K), by grant MK-5001.2015.1 of the President of the Russian Federation and DFG Grant NE~1439/3-1.

@@

\bibitem{1} P.Kuchment, \textit{Waves in Random Media}, \textbf{12}(4), R1-R24 (2002)

\bibitem{2} I.S. Lobanov, A.I. Trifanov, E.S. Trifanova, \textit{Nanosystems: Phys. Chem. Math.}, \textbf{3}(4), 512-523 (2013).

\bibitem{3} P.Exter. J.P. Keating, P. Kuchment, T. Sunada, A. Teplyaev (eds.), \textit{Analysis on Graphs and Its Applications}. Proc. Symp. Pure Math., 77 (Providence, RI: Amer. Math. Soc.) (2008)

\bibitem{4} I.Yu. Popov, A.N. Skorydina, I.V. Blinova, \textit{J. Math. Phys.}, \textbf{55}, 033504 (2014)

\bibitem{5} B. Sz.-Nagy, C. Foias, H. Bercoviuci, L. Kerchy, \textit{Harmonic Analysis of Operators on Hilbert Space}, 2nd edition, Berlin: Springer (2010)

\bibitem{6} N.K. Nikolskii, \textit{Tretise on the Shift Operator}, Berlin: Springer (1986)
